Embedded Domain Specific Languages inside Functional Languages

### 2014-03-04 paper.tex
Towards explaining deep embeddings

\subsection{QuickCheck}

@@

\cursor{}

\subsection{Lava}

\section{Example HDL DSL: Kansas Lava}
\label{sec:KansasLava}

@@

Kansas Lava~\cite{Gill:13:TypesKansasLava} is a Haskell-hosted DSL developed by the PI
that follows the Lava line of research.
It is a language for expressing gate-level circuits that can be compiled for FPGAs via VHDL.
Haskell abstractions allow the programmer to work at
a slightly higher level of abstraction, where the model
is one of recursive components communicating via synchronized streams.
Kansas Lava has been deployed for the generation of high-performance circuits for telemetry decoders,
though the model used is general.
It is a deep DSL, and therefore
has the associated restrictions.

@@

This circuit connects two multiplexers,
an adder,
and a \verb|register|
to give a circuit that counts the number of
clocked pulses on a signal \verb|inc|.
The circuit takes two clocked signals,
and returns a clocked signal that explicitly
operates using the same clock, because they
share the same type.
Notice how the use of arithmetic is understated,
but simply uses (via overloading) the
standard syntax for addition; the {\tt Num}
constraint allows this.
Figure~\ref{fig:counter-picture} gives the
circuit intended for this description.

@@

As can be seen, EDSLs are simply a way of thinking about a library.

@@

To allow us to be more specific, we now
look at two case-studies:
\begin{itemize}
\item {\bf Kansas Lava} -- recent work by the PI on a hardware description DSL;
\item and {\bf Sunroof} -- a DSL for calling and creating JavaScript, also by the PI.
%% sunroof is your work too, right?
\end{itemize}
The unifying theme is that embedded DSLs can
be pragmatic, productive and useful. We present
these to allow us to make a technical argument that adding rewrite systems to
DSLs will improve their usefulness by removing
some of the inherent and outstanding shortcomings.

@@

>>>>

\subsection{Example EDSL: QuickCheck}

@@

\section{Example EDSL: Kansas Lava}\label{sec:KansasLava}

@@

Kansas Lava~\cite{Gill:13:TypesKansasLava} is a Haskell-hosted DSL developed by the PI
that follows the Lava line of research.
Kansas Lava is a language for expressing gate-level circuits.
Haskell abstractions allow the programmer to work at
a slightly higher level of abstraction, where the model
is one of recursive components communicating via synchronized streams.
Kansas Lava has been deployed for the generation of high-performance circuits for telemetry decoders,
though the model used is general.

@@

This circuit connects two multiplexers (\verb|mux2|),
an adder,
and a \verb|register|
to give a circuit that counts the number of
clocked pulses on a signal \verb|inc|.
The circuit takes two clocked signals,
and returns a clocked signal that explicitly
operates using the same clock, because they
share the same type.
The use of arithmetic is understated,
but simply uses (via overloading) the
standard syntax for addition; the {\tt Num}
constraint allows this.
Figure~\ref{fig:counter-picture} gives the
circuit intended for this description.

@@

As can be seen, EDSLs are simply a way of thinking about a library
of provided functions, often called combinators, because they combine
their arguments into terms inside the DSL lanuage.

(((MORE))

@@

The unifying theme is that embedded DSLs can
be pragmatic, productive and useful. We present
these to allow us to make a technical argument that adding rewrite systems to
DSLs will improve their usefulness by removing
some of the inherent and outstanding shortcomings.

@@

A deeply embeeded DSL can be ...

\subsection{How to extract a deep embedding}

The basis of

\subsection{Example: Deep EDSL for Lava}
